---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# pyrfume

<!-- badges: start -->
[![R-CMD-check](https://github.com/pyrfume/rfume/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/pyrfume/rfume/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->
 
[Pyrfume](https://pyrfume.org/) is an effort to extensively curate data related to olfactory psychophysics, to transparently and automatically determine how well models make sense of this data, and to inform experimental design for olfactory research at large.

## Installation
You can install the released version of pyrfume from [CRAN](https://CRAN.R-project.org) with:

```{r}
install.packages("pyrfume")
```

You can install the development version of pyrfume from [GitHub](https://github.com/pyrfume/rfume):

```{r}
library(devtools)
install_github("pyrfume/rfume", force = TRUE)
```

## Example

This is a basic example which shows you how retrieve a behavior dataset

```{r example}

Snitz2013 <- pyrfume::load_data("snitz_2013/behavior.csv")
hist(Snitz2013$Similarity)

```

